WHOOMP! (There It Is) \\ Rapid Bayesian position reconstruction for gravitational\nobreakdashes-wave transients

### 2015-11-19 ms.tex
Fix typo

The interpolant is evaluated slightly differently depending on which of the three regions marked I, II, and II in Figure~\ref{fig:radial-integral-interpolant} contains the point of interest. In region I, we use bicubic interpolation of $\log \mathcal{G}$ in $x$ and $y$. In region II, we use univariate cubic interpolation of $\log \mathcal{G}$ in $x$, with the sample points taken from the horizontal boundary between regions I and II. In region III, we use univariate cubic interpolation of $\log \mathcal{G}$ in $u = (x - y) / 2$, with the sample points taken from the downward diagonal boundary between regions I and III. Finally, the distance integral $\mathscr{F}$ is obtained by multiplying the interpolated value of $\mathscr{G}$ by $\exp\left(p^2/{r_0}^2\right)$. For a $400\times400$ grid, the entire lookup table scheme is accurate to a relative error of about $10^{-5}$ in $\mathscr{F}$ (see Figure~\ref{fig:distance_interpolant_convergence}).

>>>>

The interpolant is evaluated slightly differently depending on which of the three regions marked I, II, and III in Figure~\ref{fig:radial-integral-interpolant} contains the point of interest. In region I, we use bicubic interpolation of $\log \mathcal{G}$ in $x$ and $y$. In region II, we use univariate cubic interpolation of $\log \mathcal{G}$ in $x$, with the sample points taken from the horizontal boundary between regions I and II. In region III, we use univariate cubic interpolation of $\log \mathcal{G}$ in $u = (x - y) / 2$, with the sample points taken from the downward diagonal boundary between regions I and III. Finally, the distance integral $\mathscr{F}$ is obtained by multiplying the interpolated value of $\mathscr{G}$ by $\exp\left(p^2/{r_0}^2\right)$. For a $400\times400$ grid, the entire lookup table scheme is accurate to a relative error of about $10^{-5}$ in $\mathscr{F}$ (see Figure~\ref{fig:distance_interpolant_convergence}).
